---
title: "hgf_results post hoc analyses"
output: html_document
date: "2024-08-22"
author : "Nazia Jassim"
---


# Posthoc analyses on HGF modelling output in relation to MRS data (processed) and questionnaire
# HGF output from the Julia modelling fitting extracted from JLD2 format and saved as .csv files 
# All data required to run these analyses can be found in the repository below: 
# Jassim, Nazia et al. (2025). Neurochemical markers # of uncertainty processing in humans. figshare. Dataset. https://doi.org/10.6084/m9.figshare.28430543


```{r}
# Load required libaries
library("tidyverse");
library("tidyr")
library("dplyr")
library("ggpubr");


## Read in output from the HGF modelling. D 

read.csv("hgf_results_summary/hgf_posteriors_all_participants.csv") -> hgf_results;

read.csv("hgf_results_summary/hgf_results_all.csv") -> hgf_results_all

read.csv("hgf_results_summary/combined_hist.csv") -> histories


read.csv("demographics_srt.csv") -> demo   # demographics
read.csv("MRS/glx_motor.csv") -> glx_motor  # mrs data

# For control MRS analyses
# read.csv("MRS/motor_gaba.csv") -> gaba_motor
# read.csv("MRS/glx_vis.csv") -> glx_vis
# read.csv("MRS/gaba_vis.csv") -> gaba_vis

```

## SUMMARY PLOTS for manuscript: Extract summary results for each beta estimate from the regression model and plot them separately
```{r}

## Regression Beta unexpected uncertainty
hgf_results %>% filter(parameters == "regression_beta_unexpected_uncertainty") -> beta_uu;

colnames(beta_uu)[c(3:9)] <- paste('beta_uu', colnames(beta_uu)[c(3:9)], sep = '_')
arrange(beta_uu, beta_uu_mean) %>% add_column(ID =1:42) -> beta_uu_arrange

beta_uu_arrange %>% ggplot(aes(x= ID, y= beta_uu_mean, ymin= beta_uu_mean-beta_uu_std, ymax= beta_uu_mean+beta_uu_std)) + geom_point(color="#33767b", size =4, fill= "#33767b", shape =18) +
    geom_errorbar(height=.2, color ="#33767b" , alpha = 0.6, linewidth=0.9) +  
  theme_minimal(base_size = 16) + ylab("Estimate")

beta_uu_arrange %>% ggplot(aes(y= ID, x= beta_uu_mean, xmin= beta_uu_mean-beta_uu_std, xmax= beta_uu_mean+beta_uu_std)) + geom_point(color="#6A5B6E", size =4, fill= "#6A5B6E", shape =18) +
    geom_errorbar(height=.2, color ="#6A5B6E" , alpha = 0.6, linewidth=0.9) +  
    theme_minimal(base_size = 16) + xlab("Mean Estimate") + ylab("Participant (ranked)")

## Regression Beta expected uncertainty
hgf_results %>% filter(parameters == "regression_beta_expected_uncertainty") -> beta_eu;
colnames(beta_eu)[c(3:9)] <- paste('beta_eu', colnames(beta_eu)[c(3:9)], sep = '_')

arrange(beta_eu, beta_eu_mean) %>% add_column(ID =1:42) -> beta_eu_arrange

beta_eu%>% ggplot(aes(x= SID, y= beta_eu_mean, ymin= beta_eu_mean-beta_eu_std, ymax= beta_eu_mean+beta_eu_std)) + geom_point(color="#33767b", size =4, fill= "#33767b", shape =18) +
    geom_errorbar(height=.2, color ="#33767b", alpha = 0.6, linewidth=0.9) +  
  theme_minimal(base_size = 16) + ylab("Estimate")

beta_eu_arrange %>% ggplot(aes(y= ID, x= beta_eu_mean, xmin= beta_eu_mean-beta_eu_std, xmax= beta_eu_mean+beta_eu_std)) + geom_point(color="#33767b", size =4, fill= "#33767b", shape =18) +
    geom_errorbar(height=.2, color ="#33767b" , alpha = 0.6, linewidth=0.9) +  
    theme_minimal(base_size = 16) + xlab("Mean Estimate") + ylab("Participant (ranked)")

# regression_beta_post_error
hgf_results %>% filter(parameters == "regression_beta_post_error") -> beta_pe;
colnames(beta_pe)[c(3:9)] <- paste("beta_pe", colnames(beta_pe)[c(3:9)], sep = '_')

beta_pe%>% ggplot(aes(x= SID, y= beta_pe_mean, ymin= beta_pe_mean-beta_pe_std, ymax= beta_pe_mean+beta_pe_std)) + geom_point(color="#33767b", size =4, fill= "#33767b", shape =18) +
    geom_errorbar(height=0.2, color ="#33767b", alpha = 0.6, linewidth=0.9) +  
  theme_minimal(base_size = 16) + ylab("Estimate")

arrange(beta_pe, beta_pe_mean) %>% add_column(ID =1:42) -> beta_pe_arrange
beta_pe_arrange %>% ggplot(aes(y= ID, x= beta_pe_mean, xmin= beta_pe_mean-beta_pe_std, xmax= beta_pe_mean+beta_pe_std)) + geom_point(color="#192A3C", size =4, fill= "#192A3C", shape =18) +
    geom_errorbar(height=.2, color = "#192A3C", alpha = 0.6, linewidth=0.9) +  
    theme_minimal(base_size = 16) + xlab("Mean Estimate") + ylab("Participant (ranked)")

hgf_results %>% filter(parameters == "regression_beta_post_reversal") -> beta_pr;
colnames(beta_pr)[c(3:9)] <- paste("beta_pr", colnames(beta_pr)[c(3:9)], sep = '_');

#regression_beta_post_reversal

merge(beta_pr, demo, by= "SID") %>% ggscatter(x = "beta_pr_mean", y="STAI_T", 
                   add = "reg.line", conf.int = TRUE, 
                   cor.coef = TRUE, cor.method = "pearson")

beta_pr_arrange %>% ggplot(aes(y= ID, x= beta_pr_mean, xmin= beta_pr_mean-beta_pr_std, xmax= beta_pr_mean+beta_pr_std)) + geom_point(color="#33767b", size =4, fill= "#33767b", shape =18) +
    geom_errorbar(height=.2, color ="#33767b" , alpha = 0.6, linewidth=0.9) +  
    theme_minimal(base_size = 16) + xlab("Mean Estimate") + ylab("Participant (ranked)")


beta_pr%>% ggplot(aes(x= SID, y= beta_pr_mean, ymin= beta_pr_mean-beta_pr_std, ymax= beta_pr_mean+beta_pr_std)) + geom_point(color="#33767b", size =4, fill= "#33767b", shape =18) +
    geom_errorbar(height=0.2, color ="#33767b", alpha = 0.6, linewidth=0.9) +  
  theme_minimal(base_size = 16) + ylab("Estimate")

## RElationship between STAI Trait and post-reversal Beta 
merge(beta_pr, demo, by= "SID") %>% ggplot(aes(x = beta_pr_mean, y=STAI_T)) +
  geom_point(size=4, shape=18 , alpha= 0.7, color = "#d66d50") +
  geom_smooth(method="lm", color = "#d66d50", fill= "#d66d50", alpha = 0.2)+ stat_cor(method = "pearson") + theme_minimal(base_size=16) +
  xlab("HGF Response Model: Session") + ylab("STAI-Trait") 
                   

merge(beta_pr, demo, by= "SID")-> pr_stai

cor.test(pr_stai$beta_pr_mean, pr_stai$STAI_T)

merge(beta_pr, glx_motor, by= "SID") %>% ggscatter(x = "beta_pr_mean", y="absolute_Glx_corr_alpha", 
                   add = "reg.line", conf.int = TRUE, 
                   cor.coef = TRUE, cor.method = "pearson")
hgf_results %>% filter(parameters == "regression_noise")  -> reg_noise;
colnames(reg_noise)[c(3:9)] <- paste('reg_noise', colnames(reg_noise)[c(3:9)], sep = '_')
merge(reg_noise, demo, by= "SID") %>% ggscatter(x = "reg_noise_mean", y="STAI_T", 
                   add = "reg.line", conf.int = TRUE, 
                   cor.coef = TRUE, cor.method = "pearson")

## regression_noise

reg_noise%>% ggplot(aes(x= SID, y= reg_noise_mean, ymin= reg_noise_mean-reg_noise_std, ymax= reg_noise_mean+ reg_noise_std)) + geom_point(color="#33767b", size =4, fill= "#33767b", shape =18) +
    geom_errorbar(height=0.2, color ="#33767b", alpha = 0.6, linewidth=0.9) +  
  theme_minimal(base_size = 16) + ylab("Estimate")

arrange(reg_noise, reg_noise_mean) %>% add_column(ID =1:42) -> reg_noise_arrange
reg_noise_arrange %>% ggplot(aes(y= ID, x= reg_noise_mean, xmin= reg_noise_mean-reg_noise_std, xmax= reg_noise_mean+reg_noise_std)) + geom_point(color="#BA5A31", size =4, fill= "#BA5A31", shape =18) +
    geom_errorbar(height=.2, color ="#BA5A31" , alpha = 0.6, linewidth=0.9) +  
    theme_minimal(base_size = 16) + xlab("Mean Estimate") + ylab("Participant (ranked)")


## Regression_beta_intercept	
hgf_results %>% filter(parameters == "regression_beta_surprise")  -> reg_surprise;
colnames(reg_surprise)[c(3:9)] <- paste('reg_surprise', colnames(reg_surprise)[c(3:9)], sep = '_');

reg_surprise%>% ggplot(aes(x= SID, y= reg_surprise_mean, ymin= reg_surprise_mean-reg_surprise_std, ymax= reg_surprise_mean+ reg_surprise_std)) + geom_point(color="#33767b", size =4, fill= "#33767b", shape =18) +
    geom_errorbar(height=0.2, color ="#33767b", alpha = 0.6, linewidth=0.9) +  
  theme_minimal(base_size = 16) + ylab("Estimate")


arrange(reg_surprise, reg_surprise_mean) %>% add_column(ID =1:42) -> reg_surprise_arrange
reg_surprise_arrange %>% ggplot(aes(y= ID, x= reg_surprise_mean, xmin= reg_surprise_mean-reg_surprise_std, xmax= reg_surprise_mean+reg_surprise_std)) + geom_point(color="#96C5BD",size =4, fill= "#96C5BD", shape =18) +
    geom_errorbar(height=.2, color ="#96C5BD", alpha = 0.6, linewidth=0.9) +  
    theme_minimal(base_size = 16) + xlab("Mean Estimate") + ylab("Participant (ranked)")

##	regression_beta_surprise

hgf_results %>% filter(parameters == "regression_beta_surprise")  -> reg_surprise;
colnames(reg_surprise)[c(3:9)] <- paste('reg_surprise', colnames(reg_surprise)[c(3:9)], sep = '_');

reg_surprise%>% ggplot(aes(x= SID, y= reg_surprise_mean, ymin= reg_surprise_mean-reg_surprise_std, ymax= reg_surprise_mean+ reg_surprise_std)) + geom_point(color="#33767b", size =4, fill= "#33767b", shape =18) +
    geom_errorbar(height=0.2, color ="#33767b", alpha = 0.6, linewidth=0.9) +  
  theme_minimal(base_size = 16) + ylab("Estimate")

# Regression_beta_surprise
arrange(reg_surprise, reg_surprise_mean) %>% add_column(ID =1:42) -> reg_surprise_arrange
reg_surprise_arrange %>% ggplot(aes(y= ID, x= reg_surprise_mean, xmin= reg_surprise_mean-reg_surprise_std, xmax= reg_surprise_mean+reg_surprise_std)) + geom_point(color="#96C5BD",size =4, fill= "#96C5BD", shape =18) +
    geom_errorbar(height=.2, color ="#96C5BD", alpha = 0.6, linewidth=0.9) +  
    theme_minimal(base_size = 16) + xlab("Mean Estimate") + ylab("Participant (ranked)")
```



#volatility beliefs
```{r}
# hgf_results %>% filter(parameters == "xprob_volatility") -> xprob_vol;
# colnames(xprob_vol)[c(3:9)] <- paste("xprob_vol", colnames(xprob_vol)[c(3:9)], sep = '_');
# 
# 
# xprob_vol%>% ggplot(aes(x= SID, y= xprob_vol_mean, ymin= xprob_vol_mean-xprob_vol_std, ymax= xprob_vol_mean+xprob_vol_std)) + geom_point(color="#d66d50", size =4, fill= "#d66d50", shape =18) +
#     geom_errorbar(height=0.2, color ="#d66d50", alpha = 0.6, linewidth=0.9) +  
#   theme_minimal(base_size = 16) + ylab("Mean estimate")
# 
# 
# merge(xprob_vol, glx_motor, by= "SID") %>% ggscatter(x = "xprob_vol_mean", y="absolute_Glx_corr_alpha", size =6, shape=18, color = "#33767b",
#                    add = "reg.line", conf.int = TRUE, 
#                    cor.coef = FALSE,
#                    cor.method = "pearson"
#                    ) + theme(text = element_text(size = 18)) + ylab("Motor Glx") 
# 
# 
# 
# merge(xprob_vol, glx_motor, by= "SID") %>% ggplot(aes(x = xprob_vol_mean, y=absolute_Glx_corr_alpha))+
#  geom_point(color = "#33767b", shape=18, size=3, alpha =0.7) +
#   geom_smooth(method = "lm", color = "#33767b", fill= "#33767b", alpha =0.2, se = TRUE) + stat_cor(method = "pearson") + theme(text = element_text(size = 18)) + theme_minimal(base_size=16)+ ylab("Motor Glx")
# 
# 
# 
# merge(xprob_vol, demo, by= "SID") %>% ggscatter(x = "xprob_vol_mean", y="STAI_T", 
#                    add = "reg.line", conf.int = TRUE, 
#                    cor.coef = TRUE, cor.method = "pearson")
# 
# merge(xprob_vol, glx_motor, by= "SID") -> glx_vol
# 
# cor.test(glx_vol$xprob_vol_mean, glx_vol$absolute_Glx_corr_alpha)
# 
# reg_noise%>% ggplot(aes(x= SID, y= reg_noise_mean, ymin= reg_noise_mean-reg_noise_std, ymax= reg_noise_mean+ reg_noise_std)) + geom_point(color="#33767b", size =4, fill= "#33767b", shape =18) +
#     geom_errorbar(height=0.2, color ="#33767b", alpha = 0.6, linewidth=0.9) +  
#   theme_minimal(base_size = 16) + ylab("Estimate")
# 
#  merge(xprob_vol, demo, by= "SID")-> d
# cor.test(d$xprob_vol_mean, d$STAI_T)
# 


```


## Summary plot : All regressors in the response model
```{r}
#merge(srt_data_avg_sid, hgf_results, by ="SID")-> hgf

hgf_results_all %>% pivot_longer(names_to = "beta_estimate", cols = 4:11) %>% filter(beta_estimate != "xprob_volatility") -> hgf_results_plot

hgf_results_plot %>% group_by(beta_estimate) %>% summarise(mean= mean(value), std= sd(value)) -> hgf_summary


hgf_summary%>% ggplot(aes(y= beta_estimate, x= mean, xmin= mean-std, xmax= mean+std)) + geom_point( size =6, color= colors1, fill= colors1, shape =18) +
    geom_errorbarh(height=.2, color =colors1 , alpha = 0.6, linewidth=0.9) +  theme_minimal(base_size = 16) + xlab("Mean Estimate") + ylab("Beta estimate")  + scale_fill_manual(values= colors1) + scale_color_manual(values= colors1) 


hgf_results_plot %>% filter(beta_estimate =="regression_beta_post_error") %>% ggplot(aes(x= value, fill= "#d66d50", color= "#d66d50")) + geom_density(alpha=0.4) + theme_minimal(base_size = 16) + xlab("B-post_error")


hgf_results_summary %>% filter(beta_estimate == group_by(beta_estimate, SID) %>% summarise(mean_= mean(value), std= sd(value))-> hgf_summary_by_SID

hgf_summary_by_SID%>% ggplot(aes(x= SID, y= mean, ymin= mean-std, ymax= mean+std)) + geom_point(color="#d66d50", size =3, fill= "#d66d50", shape =18) +
    geom_errorbar(height=.2, color ="#d66d50" , alpha = 0.6, linewidth=0.9) +  theme_minimal(base_size = 16) + xlab("Mean") + ylab("Beta estimate") + facet_wrap(~beta_estimate)

```


#one sample t test for response model parameter estimates
```{r}
# expected uncertainty beta
hgf_results%>% filter(parameters== "regression_beta_expected_uncertainty") ->eu
t.test(eu$mean, mu = 0, alternative = "two.sided");

#surprise
hgf_results%>% filter(parameters== "regression_beta_surprise") -> surprise
t.test(surprise$mean, mu = 0, alternative = "two.sided");


#post-error
hgf_results%>% filter(parameters== "regression_beta_post_error") -> pe
t.test(pe$mean, mu = 0, alternative = "two.sided");

#post_reversal
hgf_results%>% filter(parameters== "regression_beta_post_reversal") -> pr

hgf_results%>% filter(parameters== "regression_noise") -> noise;
t.test(noise$mean, mu = 0, alternative = "two.sided");
```


## HI level prediction errors
```{r}
histories %>% dplyr::select(matches("value_prediction_error"), "SID") %>% dplyr::select(matches("xprob"), "SID") -> high_PE


high_PE%>% group_by(SID) %>% mutate(Trial_number= row_number(), 
                                    Session = if_else(Trial_number == 1:960, "Pre-reversal", "Post-reversal")) %>%
  group_by(Session) %>% 
  mutate(Trial_number= row_number(), Trial = case_when(Trial_number ==1:120 ~ 120, Trial_number == 121:240 ~ 240,  Trial_number == 241:360 ~ 360, 
                          Trial_number == 361:480 ~ 480,  Trial_number== 481:600 ~ 600, 
                          Trial_number == 601:720 ~ 720,  Trial_number == 721:840~ 840, Trial_number == 841:860 ~ 960))-> high_PE_time

high_PE_time %>% group_by(Session, SID) %>% pivot_longer(names_to = "hi_pe", cols = 1:16) -> PE

#PE %>% group_by(SID, Session, Trial_number) %>% mutate(PE_per_trial = mean(value, na.rm=TRUE)) 


###### PE by block irrespectivee of category
PE %>% group_by(SID, Session, Trial) %>% mutate(PE_per_block = mean(value, na.rm=TRUE), Trial = as.factor(Trial), Session = as.factor(Session)) %>% na.omit() -> PE_block


PE_block %>%
    ggplot(aes(x = Trial , y = value, color=Session, fill=Session)) + stat_summary(geom = "line", size=1, alpha=0.8) +
    stat_summary(geom = "ribbon", fun.data = mean_cl_normal, alpha = 0.3) + theme_minimal(base_size=16) + facet_wrap(~Session)  + scale_color_manual(values= colors1) + scale_fill_manual(values= colors1)+ theme_minimal(base_size = 16) + xlab("Trial")  + ylab("Hi PE") + guides(fill=guide_legend(title="Session"), color =guide_legend(title= "Session")) 


## HI level PE matrix

PE %>% group_by(Session, hi_pe) %>% summarise(mean = mean(value, na.rm = TRUE), sd = sd(value, na.rm=TRUE)) -> hi_pe_matrix

PE %>% group_by(Session, SID) %>% summarise(mean= mean(value, na.rm=TRUE), med = median(value, na.rm=TRUE), sd= sd(value, na.rm=TRUE)) -> PE_avg

PE %>% ungroup() %>% group_by(SID) %>% summarise(mean = mean(value, na.rm = TRUE),  sd= sd(value, na.rm=TRUE)) %>% add_column(parameter = "high_level_PE") -> pe_avg_sid;


merge(pe_avg_sid, glx_motor, by ="SID") %>% ggscatter(x = "mean", y="absolute_Glx_corr_alpha", color="#d66d50", size=6, shape=18,                        
                                                        add = "reg.line", conf.int = TRUE, 
                                    cor.coef = TRUE, cor.method = "pearson")  + xlab("PE") + ylab("Motor Glx") +  theme(text = element_text(size = 18))

merge(pe_avg_sid, glx_motor, by= "SID") %>% ggplot(aes(x = mean, y=absolute_Glx_corr_alpha))+
 geom_point(color = "#d66d50", shape=18, size=3, alpha =0.7) +
  geom_smooth(method = "lm", color = "#d66d50", fill= "#d66d50", alpha =0.2, se = TRUE) + stat_cor(method = "pearson") + theme(text = element_text(size = 18)) + theme_minimal(base_size=16)+ ylab("Motor Glx") 



PE%>% ggplot(aes(x= Session, y = value, color = Session, fill = Session)) +  ggdist::stat_halfeye(adjust = .5, width = .3, justification = -.7, alpha= 0.2) + geom_boxplot(width = .2, outlier.shape = NA, linetype=1, alpha= 0.8 ) +
  #gghalves::geom_half_point(side ="l", range_scale = .3, alpha = 0.1) + 
  scale_fill_manual(values= colors1) + scale_color_manual(values= colors1) + theme_minimal(base_size = 16) + xlab("Session")  + ylab("Posterior (mean)") + guides(fill=guide_legend(title="Session"), color =guide_legend(title= "Session"))

## Correlation with metabs
merge(pe_avg_sid, glx_motor, by ="SID") -> glx_pe
cor.test(glx_pe$mean, glx_pe$absolute_Glx_corr_alpha)

# control corr with metab

merge(pe_avg_sid, gaba_motor, by ="SID") -> gaba_pe
cor.test(gaba_pe$mean, gaba_pe$absolute_GABA_corr_alpha)

merge(pe_avg_sid, glx_vis, by ="SID") -> glx_vis_pe
cor.test(glx_vis_pe$mean, glx_vis_pe$absolute_Glx_corr_alpha)

```


## Trial by trial surprise 
```{r}

read.csv("hgf_results_summary/surprises_all.csv") %>% arrange()-> surprises

surprises %>% group_by(SID) %>% summarise(mean = mean(surprise),  sd= sd(surprise), median=median(surprise)) %>% add_column(parameter ="surprise")-> surprise_avg_sid


surprises %>% group_by(SID) %>% mutate(Time = row_number(), 
                                       Session = if_else(Time == 1:958, "Pre-reversal", "Post-reversal")) %>% group_by(SID,Session) %>% 
  mutate(Trial_Number = row_number(),
        bins = case_when(Trial_Number ==1:120 ~ 120,
                         Trial_Number == 121:240 ~ 240,  Trial_Number == 241:360 ~ 360, 
                        Trial_Number == 361:480 ~ 480,  Trial_Number== 481:600 ~ 600, 
                         Trial_Number == 601:720 ~ 720,  Trial_Number == 721:840 ~ 840, Trial_Number == 841:960 ~ 960)) -> surprises_time



surprises_time$Session_temp= factor(surprises_time$Session, levels = c("Pre-reversal", "Post-reversal")) # have to do this because facet would display the post-reversal first!

 surprises_time %>%  ggplot(aes(x= bins, y= surprise, color= Session_temp, fill= Session_temp)) + 
     stat_summary( geom="pointrange", size=0.8) +  stat_summary(geom="line", size=1)+
     stat_summary(geom = "ribbon", fun.data = mean_cl_normal, alpha = 0.1) +  xlab("Trial Number") + ylab("Surprise")+
     facet_wrap(~Session_temp) +
     scale_x_continuous(breaks= c(120, 240, 360, 480, 600, 720, 840, 960))+ scale_fill_manual(values= colors1) + scale_color_manual(values= colors1) + theme_minimal(base_size = 16)   + guides(fill=guide_legend(title="Session"), color =guide_legend(title= "Session"))


surprises_time %>% group_by(SID, Session) %>% summarise(mean_surprise = mean(surprise), med_surprise = median(surprise), sd_surprise= sd(surprise)) -> surprise_avg


surprises_time$Session_temp= factor(surprises_time$Session, levels = c("Pre-reversal", "Post-reversal"))

surprises_time %>% ggplot(aes(x= Session_temp, y = surprise, color = Session_temp, fill = Session_temp)) +  ggdist::stat_halfeye(adjust = .5, width = .3, justification = -.7, alpha= 0.2) + geom_boxplot(width = .2, outlier.shape = NA, linetype=1, alpha= 0.8 ) +
  gghalves::geom_half_point(side ="l", range_scale = .3, alpha = 0.1) + 
  scale_fill_manual(values= colors1) + scale_color_manual(values= colors1) + theme_minimal(base_size = 16) + xlab("Session")  + ylab("Mean surprise") + guides(fill=guide_legend(title="Session"), color =guide_legend(title= "Session"))

ggsave("surprise.png", width=6, height=4)

 # surprises_time %>% ggplot(aes(x= Session, y= surprise, color=Session, fill=Session)) +
 #    geom_rain(alpha = .4, rain.side = 'f2x2', #id.long.var = "SID",
 #                violin.args = list(color = NA, alpha = .7)) +
 #  scale_fill_manual(values= colors1) + scale_color_manual(values= colors1) + theme_minimal(base_size = 16) + xlab("Session") + ylab("  ")

#
surprises_time %>%
    ggplot(aes(x = Time , y = surprise, color=Session_temp, fill=Session_temp)) + stat_summary(geom = "line", size=1, alpha=0.8) +
    stat_summary(geom = "ribbon", fun.data = mean_cl_normal, alpha = 0.3) + theme_minimal(base_size=16) + 
   scale_fill_manual(values= colors1) + scale_x_continuous(breaks= c(120, 960, 1920))+ 
  scale_color_manual(values= colors1) + theme_minimal(base_size = 16) + xlab("Trial")  + ylab("Mean surprise") + guides(fill=guide_legend(title="Session"), color =guide_legend(title= "Session"))


surprises_time %>%
    ggplot(aes(x = Trial_Number , y = surprise, color=Session_temp, fill=Session_temp)) + stat_summary(geom = "line", size=1, alpha=0.8) +
    stat_summary(geom = "ribbon", fun.data = mean_cl_normal, alpha = 0.3) + theme_minimal(base_size=16) + facet_wrap(~Session_temp) + scale_fill_manual(values= colors1) + scale_x_continuous(breaks= c(120, 480, 960))+ scale_color_manual(values= colors1) + theme_minimal(base_size = 16) + xlab("Trial")  + ylab("Mean surprise") + guides(fill=guide_legend(title="Session"), color =guide_legend(title= "Session"))


```



# Relationship between behavioural data and surprise
```{r}

# read srt data, exclude sid 1017 as they were excluded from modelling data
# surprise is calculated after first two trials, so delete those trials
#
srt_data %>% filter(SID !=1017) %>% group_by(SID) %>% mutate(rown =row_number()) %>% filter(rown!=1,rown!=2) %>% select(-rown, -X, -Trial_Number) %>% arrange(SID)-> tomerge

cbind(tomerge, surprises) %>% #select(-SID...18) %>%
  rename(SID= SID...1) %>% select(-SID...18)%>% group_by(SID, Session) %>% mutate(Trial_Number = row_number()) -> surprise_srt_data_combined

surprise_srt_data_combined %>% 
   mutate(Stages = as.factor(case_when(Trial_Number==1:320 ~ "Early", Trial_Number== 321:640 ~ "Middle", Trial_Number==641:960 ~ "Late")),
        bins = case_when(Block ==1 ~ 120, Block == 2 ~ 240, Block == 3 ~ 360, Block == 4 ~ 480, Block == 5 ~ 600, Block == 6 ~ 720, Block == 7 ~ 840, Block == 8 ~ 960),
          Session = case_when(Session== 1 ~ "Pre-reversal", Session == 2 ~ "Post-reversal"),
                    Session = as.factor(Session),
        Trial = case_when(post_error== 1 ~ "Post-error", post_error==0 ~ "Post-correct"),
                    Probability = as.factor(case_when(Sequence == "High Prob" ~ "High", Sequence == "Low Prob" ~ "Low"))) -> surprises_srt


surprises_srt$Session_temp= factor(surprises_srt$Session, levels = c("Pre-reversal", "Post-reversal"))
surprises_srt$Stages_temp = factor(surprises_srt$Stages, levels = c("Early", "Middle", "Late"))


surprises_srt %>% ggplot(aes(x= bins, y= surprise, group= Probability, color= Probability, fill=Probability)) + 
    stat_summary( geom="pointrange", size=0.8) +  stat_summary(geom="line", size=1)+
    stat_summary(geom = "ribbon", fun.data = mean_cl_normal, alpha = 0.1) +  xlab("Trial Number") + ylab("Surprise")+
    facet_wrap(~Session_temp) + scale_x_continuous(breaks= c(120, 240, 360, 480, 600, 720, 840, 960)) + 
    scale_fill_manual(values= colors1) + scale_color_manual(values= colors1) + theme_minimal(base_size = 16)   



model <-lmer(surprise ~ Session * Stages + (1| SID), data=surprises_srt);
summary(model)
```


### PARAMETER RECOVERY RESULTS
```{r}
 read.csv("hgf_results_summary/aggregated_param_rec_results.csv")  %>%
separate_wider_delim(results_column, delim = ",", names = c("iteration", "chain",	"rec_value", "lp","n_steps","is_accept", "acceptance_rate", "log_density", "hamiltonian_energy", "hamiltonian_energy_error", "max_hamiltonian_energy_error", "tree_depth", "numerical_error", "step_size", "nom_step_size")) %>% 
  select(c("ID", "parameter", "sim_value", "rec_value")) %>% mutate(rec_value = as.numeric(rec_value)) -> param_rec


## Volatility belief
param_rec %>% filter(parameter == "vol") -> param_rec_vol

param_rec_vol %>% group_by(ID, sim_value) %>% summarise(mean_rec_value = mean(rec_value), med_rec_value = median(rec_value)) -> param_rec_vol_avg

param_rec_vol_avg %>% ggscatter(x = "sim_value", y="med_rec_value", color="#d66d50",
                   add = "reg.line", conf.int = TRUE, 
                   cor.coef = TRUE, cor.method = "pearson") +  xlab("Generative values") + ylab("Recovered values") +  theme_minimal(base_size=16)


cor.test(param_rec_vol_avg$med_rec_value, param_rec_vol_avg$sim_value)

## Surprise
param_rec %>% filter(parameter == "surprise") -> param_rec_surprise

param_rec_surprise %>% group_by(ID, sim_value) %>% summarise(mean_surp_value = mean(rec_value), med_rec_value = median(rec_value)) -> param_rec_surprise_avg

param_rec_surprise_avg %>%ggscatter(x = "sim_value", y="med_rec_value", color="#33767b",
                   add = "reg.line", conf.int = TRUE, 
                   cor.coef = TRUE, cor.method = "pearson") +  xlab("Generative values") + ylab("Recovered values") +  theme_minimal(base_size=16)


cor.test(param_rec_surprise_avg$med_rec_value, param_rec_surprise_avg$sim_value)


## Post_error
param_rec %>% filter(parameter == "posterror") -> param_rec_pe

param_rec_pe %>% group_by(ID, sim_value) %>% summarise(mean_pe_value = mean(rec_value), med_rec_value = median(rec_value)) -> param_rec_pe_avg

param_rec_pe_avg %>%ggscatter(x = "sim_value", y="med_rec_value", color="#d66d50",
                   add = "reg.line", conf.int = TRUE, 
                   cor.coef = TRUE, cor.method = "pearson") +  xlab("Generative values") + ylab("Recovered values") +  theme_minimal(base_size=16)
cor.test(param_rec_pe_avg$sim_value, param_rec_pe_avg$med_rec_value)

# ## Expected uncertainty
param_rec %>% filter(parameter == "expecteduncertainty") -> param_rec_eu

param_rec_eu %>% group_by(ID, sim_value) %>% summarise(mean_eu_value = mean(rec_value), med_rec_value = median(rec_value)) -> param_rec_eu_avg

param_rec_eu_avg %>%ggscatter(x = "sim_value", y="med_rec_value", color="#33767b",
                              add = "reg.line", conf.int = TRUE, 
                   cor.coef = TRUE, cor.method = "pearson") +  xlab("Generative values") + ylab("Recovered values") +  theme_minimal(base_size=16)


cor.test(param_rec_eu_avg$sim_value,param_rec_eu_avg$med_rec_value)

## Unexpected uncertainty
param_rec %>% filter(parameter == "unexpecteduncertainty") -> param_rec_uu

param_rec_uu %>% group_by(ID, sim_value) %>% summarise(mean_uu_value = mean(rec_value), med_rec_value = median(rec_value)) -> param_rec_uu_avg

param_rec_uu_avg %>%ggscatter(x = "sim_value", y="med_rec_value", color="#d66d50",
                              add = "reg.line", conf.int = TRUE, 
                   cor.coef = TRUE, cor.method = "pearson") +  xlab("Generative values") + ylab("Recovered values") +  theme_minimal(base_size=16)

cor.test(param_rec_uu_avg$sim_value,param_rec_uu_avg$med_rec_value)

```



